Developing a preprint culture in biology

### 2012-10-06 ms.tex

Submission to arXiv is fully automated.  Authors can submit \TeX{}/\LaTeX{}
documents that are compiled on the server or directly submit in PDF/PS format
(for example, as exported by a word processor).  A moderation system was put in
place in 2004: papers must be categorized by an endorser. At least one author of
a paper must be an endorser that has previously submitted a paper or has
received permission to submit to a particular category.  Many authors in
mathematics and physics submit papers as soon as they are ready for review by
colleagues, although another popular option is submitting simultaneously to a
journal and arXiv.

Authors must either have their arXiv submission available under an open license
or grant arXiv a non-exclusive and irrevocable license to distribute the work.
In either case, arXiv does not require copyright transfer and only requires the
rights to distribute submitted articles in perpetuity. Thus, submitting to arXiv
does not prevent the authors from transferring their rights to a
publisher.

Most papers posted to arXiv are eventually printed in journals but there are
notable exceptions including Perelman's landmark paper leading to the proof of
the Poincar\'{e} conjecture \cite{2002math.....11159P}.  However, arXiv has
never sought to replace scientific journals and explicitly states that it serves
a different function as ``an openly accessible, moderated repository for
scholarly articles in specific scientific disciplines.'' arXiv is now
administered by the Cornell University Libraries, with funding coming from
voluntary pledges by academic institutions along with matching funds from the
Simons Foundation \cite{arxiv_future}.  One-hundred twenty six of the top
two-hundred institutions in terms of downloads have provided the operating
budget for arXiv over the next five years.  This plan reduces the financial
burden on Cornell University and transfers governance to a collaborative
community in accordance with arXiv's key principles.  arXiv takes numerous
measures to ensure that the repository will remain permanently available and
submissions will be readable.

@@

figshare (\href{http://figshare.com}{http://figshare.com}) is an open server
that allows scientists to submit any research output: manuscript, figures,
datasets, videos, theses, presentations, and so on. There are no rules to limit
what constitutes a research output and, unlike arXiv, there is no endorser
system. All figshare content has a unique digital object identifier (DOI) like
any journal article, thus offering a permanent and stable link to the content.
A flexible tag system is used to classify each item. All content can be
commented and is licensed under the Creative Commons (CC-BY) license, except
datasets which are published under CC0. The CC-BY license grants rights to
\emph{copy, distribute, display and perform the work and make derivative works
based on it only if they give the author or licensor the credits in the manner
specified by these.}  CC0 is the most permissive license and effectively puts
the work in public domain (no rights reserved) or, if it is not possible in the
given jurisdiction, provides a simple permissive license.

One of the biggest advantage of figshare over arXiv is that is it not limited to
quantitative sciences. arXiv.org has sections on quantitative biology but might
not be appropriate for non-quantitative work. With its flexible approach to
preprints, figshare offers an important alternative to arXiv for empirical
biologists. Furthermore, by allowing all types of content, figshare arguably
provides an archive for early results (e.g.: figures, lab presentations).
figshare also supports commenting on preprints.

@@

PeerJ (\href{https://peerj.com/}{https://peerj.com/}) is a new publishing system
that combines both a preprint server, and a peer reviewed journal.  It is
focused on the biological and medical sciences, which may help overcome the
perception that preprints do not have a home in biology.  PeerJ allows
commenting on posted preprints, improving the potential for pre-publication
dialog. In addition, preprints can be made private if the authors choose, and
shared only with selected colleagues. While this reduces many of the benefits of
preprints described above, it may allow some researchers who would not otherwise
post preprints to begin to explore the possibility in a manner appropriate to
their current circumstances.

In contrast to other preprint servers users cannot post unlimited public
preprints for free. One preprint per year can be posted for free and a onetime
(i.e. lifetime) fee of 99 dollars allows the submitting author to post unlimited public
preprints. It is also worth noting that the preprint server is not tied to the
journal, so preprints can be posted regardless of where they will eventually be
submitted for publication.

PeerJ uses the CC-BY-SA 3.0 license, which is similar to the CC-BY license used
by figshare but adds the \emph{Share-alike} (sa) restriction that derivate works
need a license identical to the license that governs the original work.

@@

F1000Research is not a public preprint server like the previous three servers.
Whereas arXiv, figshare, and PeerJ offer an option to submit a manuscript
without having it reviewed, papers submitted to F1000Research will eventually be
reviewed. Thus, F1000Research offers a hybrid model with publicly available
manuscripts at time of submission and standard peer-reviews. Manuscripts are
considered ``accepted'' and will only be indexed after two positive referee
response. F1000Research works closely with data providers to integrate raw
data to the paper. For instance, upon submitting a paper, authors are asked to
upload their data, which are then integrated in \emph{e.g.} figshare widgets,
the DOI of which are given in the paper when the data are first mentionned.
The licensing of the data is similar to that used by FigShare, meaning that
the articles are free to access, and can be redistributed readily. By
integrating data to the paper, F1000Research is working to make
science more reproducible and open.

>>>>

One aspect of arXiv that differs from other options is that it has a moderation
system, which requires that papers must be categorized by an endorser.
At least one author of a paper must be an endorser that has previously submitted
a paper or has received permission to submit to a particular category. arXiv is now
administered by the Cornell University Libraries, with funding coming from
voluntary pledges by academic institutions along with matching funds from the
Simons Foundation \cite{arxiv_future}. This approach to financing is one of
the numerous measures that arXiv takes to ensure that the repository will remain
permanently available and submissions will be readable.

@@

figshare (\href{http://figshare.com}{http://figshare.com}) is an open server
that allows scientists to submit any research output: manuscript, figures,
datasets, videos, theses, presentations, and so on. There are no rules to limit
what constitutes a research output and, unlike arXiv, there is no endorser
system. All figshare content has a unique digital object identifier (DOI) like
any journal article, thus offering a permanent and stable link to the content.
A flexible tag system is used to classify each item. Comments can be made on all
content allowing for centralized discussion related to the material.

One of the advantages of figshare over arXiv for biologists is that is it not limited
to quantitative sciences. arXiv.org has sections on quantitative biology but might
not be appropriate for non-quantitative work. With its flexible approach to
preprints, figshare offers an alternative to arXiv for empirical
biologists. Furthermore, by allowing all types of content, figshare also
provides an archive for early results (e.g.: figures, lab presentations).

@@

PeerJ (\href{https://peerj.com/}{https://peerj.com/}) is a new Open Access
publisher that combines both a preprint server, and a peer reviewed journal.
It is focused on the biological and medical sciences, which may help overcome the
perception that preprints do not have a place in biology. Like figshare this is
an advantage relative to arXiv for biologists doing non-quantitative work.
Also like figshare PeerJ allows commenting on posted preprints, improving the
potential for pre-publication
dialog. In addition, preprints can be made private if the authors choose, and
shared only with selected colleagues. While this reduces many of the benefits of
preprints described above, it may allow some researchers who would not otherwise
post preprints to begin to explore the possibility in a manner appropriate to
their current circumstances.

In contrast to other preprint servers users cannot post unlimited public
preprints for free. One preprint per year can be posted for free, with a onetime
(i.e. lifetime) fee of 99 dollars required to allow an author to post unlimited public
preprints. The preprint server is not tied to the journal, so preprints can be posted
regardless of where they will eventually be submitted for publication.

@@

F1000Research is not a public preprint server like the previous three servers.
Whereas arXiv, figshare, and PeerJ offer an option to submit a manuscript
without having it reviewed, papers submitted to F1000Research will eventually be
reviewed. Thus, F1000Research offers a hybrid model with publicly available
manuscripts at time of submission and standard peer-reviews that occur as part
of the submission process. Manuscripts are
considered ``accepted'' and will only be indexed after two positive referee
responses. F1000Research works closely with data providers to integrate raw
data to the paper. For instance, upon submitting a paper, authors are asked to
upload their data, which are then integrated in \emph{e.g.} figshare widgets,
the DOI of which are given in the paper when the data are first mentionned.
By integrating data to the paper, F1000Research is working to make
science more reproducible and open.
